Stock forecasting algorithms and their usage

### 2015-06-12 Paper_self.tex
corrections on Paper

One very important thing that to observe is influence of international newscasts. If the global economy, or even the economy of a single country is experiencing a financial crisis, the stock market will follow that trend. But those trends are most likely to be relatively slow and easy to predict even looking at the stock prices itself. What is more dangerous are catastrophes. After a catastrophe there is often a low point on the stock market. This low point comes so fast, that only algorithms that observe the news have a chance to prevent huge losses.

Another to note is, that we did all our tests on historic data of the stock market. Even if we \textit{bought} a stock at some specific point of time, we did not really buy this stock on the real market. So our tests did not affect the stock market at all. Because buying and selling stocks on the market while testing, would always affect the received results.

>>>>

One very important thing is to observe the international newscasts. If the global economy, or even the economy of a single country is experiencing a financial crisis, the stock market will follow that trend. But those trends are most likely to be relatively slow and easy to predict even looking at the stock prices itself. What is more dangerous are catastrophes. After a catastrophe there is often a low point on the stock market. This low point comes so fast, that only algorithms that observe the news have a chance to prevent huge losses.

Another thing to note is, that we did all our tests on historic data of the stock market. Even if we \textit{bought} a stock at some specific point of time, we did not really buy this stock on the real market. So our tests did not affect the stock market at all. Because buying and selling stocks on the market while testing, would always affect the received results.
